Problem Set 1 (Answers)

### 2019-09-26 static/homeworks/01-problem-set-answers.Rmd
Update problem set 1 answers and R file

```{r}
babynames %>%
  group_by(year) %>%
  filter(sex == "M",
         year>1980) %>%
  arrange(desc(n))%>%
  slice(1) # take first row only
```

@@

```{r}
babynames %>%
  group_by(year) %>%
  filter(sex == "F",
         year>1980) %>%
  arrange(desc(n))%>%
  slice(1) # take first row only
```

## Question 6
**Now let's graph the evolution of the most common names since 1880.**
### Part A
**First, find out what are the top 10 *overall* most popular names for boys and for girls. You may want to create two vectors, each with these top 5 names.**

```{r}
babynames %>%
  group_by(name) %>%
  filter(sex=="M") %>%
  summarize(total=sum(n)) %>%
  arrange(desc(total)) %>%
  slice(1:5)

# make a vector of the names (we'll need this for our graph below)
top_boys_names<-c("James", "John", "Robert", "Michael", "William")
```

```{r}
babynames %>%
  group_by(name) %>%
  filter(sex=="F") %>%
  summarize(total=sum(n)) %>%
  arrange(desc(total)) %>%
  slice(1:5)

# make a vector of the names (we'll need this for our graph below)
top_girls_names<-c("Mary", "Elizabeth", "Patricia", "Jennifer", "Linda")
```

>>>>

```{r}
babynames %>%
  group_by(year) %>% # we want one observation per year
  filter(sex == "M",
         year>1979) %>% # or >==1980
  arrange(desc(n))%>% # start with largest n first
  slice(1) # take first row only
```

@@

```{r}
babynames %>%
  group_by(year) %>% # we want one observation per year
  filter(sex == "F",
         year>1979) %>% # or >==1980
  arrange(desc(n))%>% # start with largest n first
  slice(1) # take first row only
```

## Question 6
**Now let's graph the evolution of the most common names since 1880.**

### Part A

**First, find out what are the top 10 *overall* most popular names for boys and for girls. You may want to create two vectors, each with these top 5 names.**

```{r}
babynames %>%
  group_by(name) %>% # we want one row per name
  filter(sex=="M") %>%
  summarize(total=sum(n)) %>% # add upp all of the n's for all years for each name
  arrange(desc(total)) %>% # list largest total first
  slice(1:5)

# make a vector of the names (we'll need this for our graph below)
top_boys_names<-c("James", "John", "Robert", "Michael", "William")

# you could alternatively add a command, %>% pull(name) to the first chunk of code, and it would do the same thing, but we'd want to save it, for example:

babynames %>%
  group_by(name) %>% # we want one row per name
  filter(sex=="M") %>%
  summarize(total=sum(n)) %>% # add upp all of the n's for all years for each name
  arrange(desc(total)) %>% # list largest total first
  slice(1:5) %>%
  pull(name)

```{r}
babynames %>%
  group_by(name) %>% # we want one row per name
  filter(sex=="F") %>%
  summarize(total=sum(n)) %>% # add upp all of the n's for all years for each name
  arrange(desc(total)) %>% # list largest total first
  slice(1:5)

# make a vector of the names (we'll need this for our graph below)
top_girls_names<-c("Mary", "Elizabeth", "Patricia", "Jennifer", "Linda")

# you could alternatively add a command, %>% pull(name) to the first chunk of code, and it would do the same thing, but we'd want to save it
```
